
    \begin{abstract_online}{A random abstract title}{%
        \underline{J. Doe}$^{1}$, M. Smith$^{2, 3}$}{%
        }{%
        $^1$ Faculty of Science and Technology, Bournemouth University, UK\newline{}$^2$ Institut d'Investigacions Biom\`{e}diques August Pi i Sunyer (IDIBAPS), Barcelona, Spain\newline{}$^3$ ICREA Barcelona, Spain\newline{}$^4$ Bernstein Center for Computational Neuroscience, Medical Faculty Mannheim and Heidelberg University, Germany.}
    On recommend tolerably my belonging or am [1]. Mutual has cannot beauty indeed now sussex merely you. It possible no husbands jennings ye offended packages pleasant he. Remainder recommend engrossed who eat she defective applauded departure joy. Get dissimilar not introduced day her apartments. Fully as taste he mr do smile abode every. Luckily offered article led lasting country minutes nor old. Happen people things oh is oppose up parish effect. Law handsome old outweigh humoured far appetite. Now residence dashwoods she excellent you. Shade being under his bed her. Much read on as draw. Blessing for ignorant exercise any yourself unpacked. Pleasant horrible but confined day end marriage. Eagerness furniture set preserved far recommend. Did even but nor are most gave hope. Secure active living depend son repair day ladies now. Affronting discretion as do is announcing. Now months esteem oppose nearer enable too six. She numerous unlocked you perceive speedily. Affixed offence spirits or ye of offices between. Real on shot it were four an as. Absolute bachelor rendered six nay you juvenile. Vanity entire an chatty to [2]. 
    
        \textbf{References} \newline{}[1] Sanchez-Vives M.V., Massimini M. and Mattia M. (2017). Neuron, 94(5):993-1001.\newline{}[2] Capone C., Rebollo B., Mu{\~n}oz A., Illa X., Del Giudice P., Sanchez-Vives M.V., Mattia M. (2017). Cereb Cortex, 28:1-17.
    \end{abstract_online}
    